Higher-Order unification for free!

### 2024-07-24 paper/paper_for_taps/source/main.tex
update metadata paper

\setcopyright{acmlicensed}  %
\copyrightyear{2024}
\acmYear{2024}
\acmDOI{10.1145/NNNNNNN.NNNNNNN}  % leave as is for now
\acmConference[PPDP '24]{PPDP '24}{September 10-11, 2024}{Milano, Italy}
\acmBooktitle{Proceedings of the 26th Symposium on Principles and Practice of Declarative Programming, PPDP 2024, Milano, Italy, September 10-11, 2024}
\acmPrice{15.00}
\acmISBN{9-8-4007-0969-297}

>>>>

\setcopyright{acmlicensed}  %
\copyrightyear{2024}
\acmYear{2024}
\setcopyright{rightsretained}
\acmConference[PPDP 2024]{26th International Symposium on Principles and Practice of Declarative Programming}{September 09--11, 2024}{Milano, Italy}
\acmBooktitle{26th International Symposium on Principles and Practice of Declarative Programming (PPDP 2024), September 09--11, 2024, Milano, Italy}
\acmPrice{}
\acmDOI{10.1145/3678232.3678233}
\acmISBN{979-8-4007-0969-2/24/09}
